\documentclass[11pt, a4paper]{article}
\include{cvstyle}
%

%% Headers and footers
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
% Headings
\fancyhead[L]{}
\fancyhead[C]{}
\fancyhead[R]{}

% Foot
\fancyfoot[L]{\textsf{\textcolor{colheadfoot}{CV Florence D\'ebarre} }}

\fancyfoot[C]{\textsf{\textcolor{colheadfoot}{CV-- \upshape Page} {\thepage} \textcolor{colheadfoot}{of \pageref*{LastPage}}}}

\fancyfoot[R]{\textcolor{colheadfoot}{\textsf{Updated 2016-03-31}}}

%
%
%
% ================================== DOCUMENT ==================================
%
%
%
%
\begin{document}

\section*{CV}
\begin{center}
{Florence (Flo) D\'ebarre}\\ \vspace{0.5em}
\begin{tabular}{l}
email: \textsf{\href{mailto:florence.debarre@normalesup.org}{florence.debarre@normalesup.org}} \vspace{-0.15em} \\ 
%
web: \textsf{\href{http://www.normalesup.org/~fdebarre/}{http://www.normalesup.org/\textasciitilde fdebarre/}} \vspace{0.25em} \\
%
\small Google Scholar: \textsf{\url{http://scholar.google.com/citations?user=WkZgrYsAAAAJ}}\vspace{-0.15em}\\
%
\small ORCID: \textsf{\href{http://orcid.org/0000-0003-2497-833X}{0000-0003-2497-833X}}\vspace{-0.15em}\\
%
\small Scopus Author ID: \textsf{\href{http://www.scopus.com/authid/detail.url?authorId=22233654600}{22233654600}
}\\
%
\small Address: \parbox[t]{0.7\textwidth}{\raggedright
Centre Interdisciplinaire de Recherche en Biologie (CIRB)\\
Coll\`ege de France\\
CNRS UMR 7241-- Inserm U1050\\
11, Place Marcelin Berthelot\\
75231 Paris Cedex 05, France
}
\end{tabular}


\end{center}
%
%
%
\subsection*{Academic appointments}

\begin{mytabular}
2015--\dots & Permanent researcher at the Centre for Interdisciplinary Research in Biology, Paris. \fund{ANR grant (PI), CNRS.}\\
% 
2014--2015 & Fellow of the College of Life Sciences, Wissenschaftskolleg zu Berlin (Germany).\\

2013--2015 & Lecturer in Evolutionary Theory, University of Exeter, Cornwall campus (UK).\\

2012--2013 & Biodiversity Postdoctoral Fellow, 
University of British Columbia, Vancouver (Canada).\fund{NSERC-CREATE through UBC Biodiversity Research Centre.}\\

2011--2012 & Postdoc with M. Doebeli and S. Nuismer, 
University of British Columbia, Vancouver (Canada) and University of Idaho, Moscow (USA). %\newline
\fund{NSF Grant to S. Nuismer.}\\
\end{mytabular}
%
%
%
\subsection*{Education}

\begin{mytabular}
2007--2010 & PhD in Theoretical Evolutionary Ecology (Universit\'e Montpellier II and Centre for Functional and Evolutionary Ecology (CEFE), France); Advisor: S. Gandon. \\
2005--2007 & MSc in Ecology and Evolution (\'Ecole Normale Sup\'erieure  and Universit\'e Paris 6). \newline
\small \phantom{a}M2 thesis supervised by S. Gandon and T. Lenormand, Montpellier (FR) [5 months in 2007].\vspace{-0.\baselineskip} \newline
\phantom{a}M1 thesis supervised by S. Bonhoeffer and R. Regoes, ETH Z\"urich (CH) [5 months in 2006]; \\
2004--2005 & BSc in Biology (\'Ecole Normale Sup\'erieure, Paris, France).\newline
\small \phantom{a}BSc thesis supervised by C. de Mazancourt, Imperial College (UK) [2 months in 2005].
\end{mytabular}


\subsection*{Teaching and Student supervision}

\subsubsection*{Teaching}

\begin{mytabular}
Spring 2014 & Trends in Ecology and Evolution, (BIO3131, Exeter). Module leader. \\
04/2013 & Two lectures in Quantitative Methods in Ecology and Evolution, (Biology 501, UBC). \\
01/2013 & Guest lectures on Game theory, in Evolutionary Ecology (Biology 418, UBC). \\
2011 & \textit{Qualification aux fonctions de Ma\^itre de Conf\'erences} \newline (= certification to teach at the level of an Assistant Professor in France) \\
2008--2011 & Teaching assistant (\textit{monitorat}) at Universit\'e Montpellier 2 (96h per year) \vspace{-0.15em}\\
&-- Introduction to Organismal Biology, lab instruction (1st year students) \newline
-- Introduction to Ecology, tutorials and lab instruction (2nd and 3rd year students)
\end{mytabular}


\subsubsection*{Student supervision}

\begin{mytabular}
2016--\dots & Co-supervision of Fran\c cois Bienvenu's PhD.\\
2014 & Co-supervision of Joseph Denton's MSc thesis.\\
2013--2014 & Supervision of the final projects of three undergraduate students. \\
2011 & Co-supervision of Fanny Gascuel's MSc thesis.
\end{mytabular}

\subsection*{Publications}

{\noindent \footnotesize Please check my Google Scholar profile, at %\vspace{-0.25\baselineskip}\\
 \url{http://scholar.google.ca/citations?user=WkZgrYsAAAAJ}, for bibliometrics.}

\subsubsection*{Peer-reviewed articles}

\begin{mytabular}
\npub{16} \label{DO15} & \austy{D\'ebarre F}, Otto SP, Evolutionary dynamics of a quantitative trait in a finite asexual population. \journal{Theoretical Population Biology} 108 75--88.\\
%
\npub{15} \label{DYG15} & Massol F, \austy{D\'ebarre F}, Evolution of dispersal in spatially and temporally variable environments: the importance of life cycles, \journal{Evolution} 69: 1925--1937. \\
%
\npub{14} \label{DYG15} & \austy{D\'ebarre F}, Yeaman S, Guillaume F, Evolution of quantitative traits under a migration-selection balance: when does skew matter?, \journal{The American Naturalist} 186 S37--S47. \\
%
\npub{13} \label{D15} & \austy{D\'ebarre F} Fitness costs in spatially structured environments. \journal{Evolution} 69: 1329-1335. \\

\npub{12} \label{DND14} & \austy{D\'ebarre F}, Nuismer SL, Doebeli M (2014) Multidimensional (co)evolutionary stability. \journal{The American Naturalist} 184(2): 158-171. \\
%
\npub{11} \label{DHD14} & \austy{D\'ebarre F}, Hauert C, Doebeli M (2014) Social evolution in structured populations. \journal{Nature Communications} 5: 3409 doi:10.1038/ncomms4409.\\
%
\npub{10} \label{V14} & Vines TH, Albert AYK, Andrew RL, \austy{D\'ebarre F}, Bock DG, Franklin MT, Gilbert KJ, Moore J-S, Renaut S, Rennison DJ (2014) The availability of research data declines rapidly with article age. \journal{Current Biology} 24(1): 94-97.\\
%
\npub{9} \label{G13} & Gascuel F$^M$, Choisy M, Duplantier J-M, \austy{D\'ebarre F}$^*$, Brouat C$^*$ (2013) Host Resistance, Population Structure and the Long-Term Persistence of Bubonic Plague: Contributions of a Modelling Approach in the Malagasy Focus, \journal{PLoS Computational Biology} 9(5): e1003039. \newline {\footnotesize $^M$ Master student; $^*$ Equal contribution in supervising the study.} \\
%
\npub{8} \label{DRG13} & \austy{D\'ebarre F}, Ronce O, Gandon S (2013) Quantifying the effects of migration and mutation on
adaptation and demography in spatially heterogeneous environments, \journal{Journal of Evolutionary Biology} 26(6): 1185-1202. \\

\npub{7} \label{D12} & \austy{D\'ebarre F} (2012) Refining the conditions for sympatric ecological speciation, \journal{Journal of Evolutionary Biology} 25(12): 2651-2660.  \\
%
%%%%%%%%%%
\npub{6} \label{DLBG12} & \austy{D\'ebarre F}, Lion S, van Baalen M, Gandon S (2012) Evolution of host life-history traits in a spatially structured host-parasite system, \journal{The American Naturalist} 179(1): 52-63.  \\
%
 %%%%%%%%%%
\npub{5} \label{DL11} & \austy{D\'ebarre F}, Lenormand T (2011) Distance-limited dispersal promotes coexistence at habitat boundaries: 
reconsidering the competitive exclusion principle. \journal{Ecology Letters} 14(3): 260-266. \\
%
 %%%%%%%%%%
\npub{4} \label{DG11} & \austy{D\'ebarre F}, Gandon S (2011) Evolution in heterogeneous environments: between soft and hard selection. \journal{The American Naturalist} 177(3): E84-E97. \\
%
\npub{3} \label{DG10} & \austy{D\'ebarre F}, Gandon S (2010) Evolution of specialization in a spatially continuous environment. \journal{Journal of Evolutionary Biology} 23:1090-1099. \\
%	
\npub{2} \label{D09} & \austy{D\'ebarre F}, Lenormand T, Gandon S (2009) Evolutionary Epidemiology of Drug-Resistance in Space \journal{
PLoS Computational Biology} 5(4): e1000337. \\
%
\npub{1} \label{D07} & \austy{D\'ebarre F}, Bonhoeffer S, Regoes RR (2007) The effect of population structure on the emergence of drug resistance during influenza pandemics \journal{J R Soc Interface} 4(16): 893-906 	
\end{mytabular}
%
%
%\mysubsec{Manuscripts}
%%
%\begin{mytabular}
%%
%\nsub{1} \label{D13c} & \austy{D{\'e}barre F}, Yeaman S, Guillaume F; Skew matters: predicting mean population divergence under a migration–selection balance, \textit{in revision}.\\
%%
%\nsub{2} \label{D13e} & \austy{D{\'e}barre F}, Hauert C, Doebeli M; Social evolution in structured populations, \textit{in revision}.
%\end{mytabular}
%%

\subsubsection*{Chapters in collective volumes}

\noindent \begin{mytabular}
\nbub{1} \label{D08} & \austy{D\'ebarre F} and Gandon S (2008) \'Epid\'emiologie \'evolutive des maladies infectieuses. \textit{In} Introduction \`a l'\'Epid\'emiologie Int\'egrative des Maladies Infectieuses et Parasitaires (eds. Gu\'egan J-F \& Choisy M), pp.~347-374.
De Boeck Universit\'e, Collection Masters, Louvain-la-Neuve, Belgique. 	
\end{mytabular}


\subsection*{Conferences and seminars}

\subsubsection*{Conferences}

\begin{mytabular}
August 2015 & Talk, European Society for Evolutionary Biology meeting, Lausanne (CH).\\
%
July 2015 & Talk, Society for Molecular Biology and Evolution meeting, Vienna (AT). \\
%
July 2015 & Invited talk, Mathematical Models in Ecology and Evolution, Paris (FR). \\
%
June 2015 & Invited talk, Models in Ecology and Evolution, Montpellier (FR).\\
%
April 2015 & Invited talk, Modelling Biological Evolution 2015, Leicester (UK).\\
%
Dec 2014 & Talk, British Ecological Society-Soci\'et\'e Française d'\'Ecologie, Lille (FR).\\
%
June 2014 & Invited talk%: \stage{}
, Evolution, Raleigh, NC (USA)\\
%
June 2014 & Invited talk%: \stage{}
, ECMTB meeting, Gothenburg (Sweden)\\
%
Jan 2014 & Poster%: \stage{Population subdivision and frequency-dependent selection}
, PopGroup meeting, Bath (UK)\\
%
Sept 2013 & Talk%: \stage{Minimal branching population size}
, Workshop ``Mathematics for an Evolving Biodiversity'', Montr\'eal, QC (Canada) \\
%
June 2013 & Talk%: \stage{Social evolution in structured populations}
, Evolution, Snowbird, UT (USA) \\
%
May 2013 & Talk%: \stage{Quantifying the effects of migration and mutation on adaptation and demography in spatially heterogeneous environments}
, CSEE, Kelowna, BC (Canada)\\
%
March 2013 &	Invited Talk%: \stage{Migration--mutation--selection balance in a spatially heterogeneous environment}
, Workshop ``Biological invasions and evolutionary biology%, stochastic and deterministic models
'', Lyon (FR) \\
%
Jan 2013 & Poster%: \stage{Spatial structure and the evolution of altruistic host defense strategies}
, Workshop ``Disease Dynamics 2013%: Immunization, a true multi-scale problem
'', UBC, Vancouver (Canada) \\
%
July 2012 &	Talk%: \stage{Trait dimensionality and victim-exploiter coevolution: why Road Runner runs faster when there are multiple roads}
, Evolution-ESEB joint meeting, Ottawa (Canada) \\
%
May 2012 &	Talk%: \stage{Trait dimensionality and victim-exploiter coevolution: why Road Runner runs faster when there are multiple roads}
, Evo-WIBO, Port Townsend, WA (USA) \\
%
Nov 2011 &	Talk%: \stage{Spatial structure and the evolution of altruistic host defense strategies}
, SFU-UBC-UVic Ecology and Evolution Retreat, Brackendale (Canada) \\
%
Aug 2011 &	Talk%: \stage{Spatial structure and the evolution of altruistic host defense strategies}
, 
ESEB XIII Congress, T\"ubingen (Germany) \\
%
May 2011 & Talk% (in French): \stage{Migration load and the evolution of the genetic variance}
, Workshop on Quantitative Genetics, La Colle s/ Loup (France) \\
%
June 2010 & Talk% (in French): \stage{Between hard and soft selection: evolution of a subdivided population}
, Models in Evolutionary Ecology Workshop, Montpellier (France)\\
%
Aug 2009 &	Talk%: \stage{Evolution of specialist vs. generalist strategies in a continuous environment}
, 
ESEB XII Congress, Torino (Italy) \\
%
Oct 2008 &	Talk%: \stage{Evolutionary epidemiology of drug-resistance in space}
, ``$R_0$ and related concepts'' meeting, Paris (France) \\
%
Aug 2008 &	Talk% (in French): \stage{Evolution of Generalism}
, ``Petit Pois D\'erid\'e'' French Population Genetics Meeting, Rennes (France)\\
%
Sep 2007 &	Poster%: \stage{Which spatial pattern of treatment would best prevent the propagation of drug-resistance?}
, 
Jacques Monod Conference, Roscoff (France) \\
%
Aug 2007 &	Talk%: \stage{Evolutionary epidemiology of drug-resistance in a spatial model}
, 
ESEB XI Congress, Uppsala (Sweden) 
\end{mytabular}

\subsubsection*{Seminars}

{\noindent \footnotesize The department or lab is indicated between $[\,]$.}

\begin{mytabular}
March 2016 & Universit\'e Paris 6 [Laboratoire Jacques-Louis Lions] Paris (FR)\\
June 2015 & Max Planck Institute for Evolutionary Biology, Pl\"on (DE)\\
Nov 2014 & Wissenschaftskolleg zu Berlin (DE)\\
July 2014 & Universit\'e de Lille [Ecology-Evolution] (France)\\
May 2014 & University of Basel [Ecology-Evolution] (Switzerland)\\
May 2014 & University of Lausanne [Ecology-Evolution] (Switzerland)\\
March 2014 &   University of Zurich [Ecology-Evolution] (Switzerland) \\
March 2013 &	University of Helsinki [Mathematical Biology] (Finland) \\
Feb 2013 &	University of Idaho [Biology] (USA) \\
%\textcolor{upcoming}{Dec 2012} &	\textcolor{upcoming}{CEFE--CNRS, Montpellier [Evolutionary genetics lab] (France)} \\
Nov 2012 &	Simon Fraser University [Biophysics] (Canada) \\
Oct 2012 &	Yale University [Jetz lab] (USA) \\
Sep 2012 &	University of British Columbia [Ecology-Evolution, External seminar] (Canada) \\
March 2012 &	University of Texas, Austin [Kirkpatrick lab] (USA) \\
Jan 2012 &	University of Toronto [Ecology-Evolution] (Canada) \\
Oct 2011 &	University of British Columbia [Ecology-Evolution, Internal seminar] (Canada) \\
Sep 2011 &	University of British Columbia [Mathematics] (Canada) \\
Apr 2011 &	INSA Lyon [Computer Science \& Biology] (France) \\
Jan 2011 &	Institut des Sciences de l'\'Evolution [Ecology-Evolution], Montpellier (France) \\
\end{mytabular}
%

\subsection*{Grants and awards}

\subsubsection*{Grants, fellowships, scholarships}

\begin{mytabular}
2014 & Agence Nationale de la recherche, ANR-14-ACHN-0003 ``MOLA'' (4+1 years).\\
2014 & College of the Life Sciences Fellowship, Wissenschaftskolleg zu Berlin. \pounds 20$\,$315. \\
2014 & Travel award for International Cooperation, Universit\'e de Lille, with Fran\c{c}ois Massol. 3000 \euro. \\
2012 & 2-year Biodiversity Postdoctoral Fellowship, Biodiversity Research Centre, UBC, CA\$100$\,$000. 
\\
%
2007 & 3-year PhD Fellowship (\textit{Allocation moniteur normalien}).
 \\
%
2004 & 4-year Scholarship, \'Ecole Normale Sup\'erieure. {\small (Provides recipients with a status of Civil Servant, a full salary and is awarded to the top 20 Biology/Geology students in France.)}
\end{mytabular}

\subsubsection*{Prizes and Awards}

\begin{mytabular}
June 2014 & Springer Best talk prize, 9th European Conference for Mathematical and Theoretical Biology (ECMTB 2014, Gothenburg, Sweden).\\
Jan 2013 & Best poster prize, Workshop ``Disease Dynamics 2013: Immunization, a true multi-scale problem'' (UBC, Canada).\\
2012 & Soci\'et\'e Fran\c caise d'\'Ecologie's (SF\'E) Young investigator Award. \\
%
%\\
\end{mytabular}

\subsection*{Professional service}


\subsubsection*{Reviewing}

\begin{mytabular}
2007--\dots &Referee for \journal{Science}$^*$, \journal{Proceedings of the Royal Society B}$^{***}$, \journal{PNAS}, \journal{Ecology Letters}$^{*}$, \journal{Nature Communications}$^{*}$, \journal{Evolution}$^{**}$, \journal{The American Naturalist}$^{***}$, \journal{PLOS Biology}, \journal{PLOS Computational Biology}$^{*}$, \journal{PLOS One}$^{*}$, \journal{Journal of Theoretical Biology}$^{***}$, \journal{Evolutionary Applications}, \journal{Philosophical Transactions of the Royal Society}, \journal{Theoretical Population Biology}$^*$, \journal{BMC
Evolutionary Biology}, \journal{Scientific Reports}, \journal{Oikos}$^{*}$, \journal{Biology Letters}, \journal{Axios Reviews}.\vspace{0.25em}\newline
{\scriptsize $^{*}$: more than once, $^{**}$: more than 5 times, $^{***}$: more than 10 times; for a total of 81 reviews on 2016-03-30 }\newline
%
Reviewer of 12 chapters of ``The Analysis of Biological Data'' (2nd ed.) by Whitlock \& Schluter (Roberts and Company Publishers). \newline
Reviewer of ``The Theory of Coevolution'' by Nuismer (Roberts and Company Publishers). \\
%
2010&Top referee for \journal{Proceedings B}.
\end{mytabular}

\subsubsection*{Organization of meetings, workshops and symposia}

\begin{mytabular}
{August 2015} & {Co-organizer (with N. Rode et F. Blanquart) of a symposium
``Adaptation in heterogeneous environments: insights from host-parasite
systems'' at the ESEB 2015 meeting in Lausanne (CH).}\\
Dec 2014 &  Co-organizer (with F. Massol, CNRS \& Univ. Lille, FR) of a symposium on ``Eco-evolutionary feedbacks: theoretical and empirical perspectives'' at the joint meeting of the British Ecological Society (BES) and the Soci\'et\'e Fran\c{c}aise d'\'Ecologie (SF\'E) in Lille (FR).\\
Oct 2013 &	Co-organizer of the 2013 UBC/SFU/UVic Ecology and Evolution Retreat (Canada).\\
Oct 2012 &	Co-organizer of the 2012 UBC/SFU/UVic Ecology and Evolution Retreat (Canada).\\
June 2010 &	Founding member and co-organizer of the student workshop ``Models in Evolutionary Ecology'' in Montpellier (FR) (the fifth edition took place in June 2014). \\
\end{mytabular}

\subsubsection*{Organized seminars and journal clubs}

\begin{mytabular}
2012--2013 &	Organizer of the Biodiversity Lunchtime Internal Seminar Series (BLISS) at UBC, Vancouver (Canada).\\
2011--2013 &	Running the ``Let's Assume'' theory Journal Club at UBC (Canada).\\
2008--2009 &	Founding member and organizer of the department's bimonthly student seminar. \\
March 2009 & Organizer of the department's fourth yearly ``PhD students meeting'', CEFE, Montpellier (FR).
\end{mytabular}

\subsection*{Others}
\begin{mytabular}
Languages & French: mother tongue \newline
  English: fluent \newline 
  German: good working knowledge \\
Computing & Working with R, Mathematica, C and Matlab \\
Citizenship & French \\
%Other interests & Hiking and skiing, choir singing, modular origami
\end{mytabular}

\end{document}

